Field trial of programmable L3 VPN service deployment using SDN-Based Multi-domain Service Provisioning over IP/Optical networks

### 2021-05-14 main.tex

\begin{IEEEbiography}
[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{1010179793S.jpg}}]%
{Samier Barguil} (M.Sc. 2018). PhD Candidate from the Universidad Autonoma de Madrid. Electronic Engineer from the District University of Bogot\'a Franscisco José de Caldas and Master in Science in Industrial Automation of the Universidad Nacional de Colombia. Currently is the IP SDN Technical Leader at Wipro Technologies Ltd.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{victor.jpg}}]%
{Víctor López} (M.Sc. 2005 - Ph.D. 2009) is a Technology Expert at Systems and Network Global Direction in Telefónica gCTIO. He works on the global IP and transport processes of the Telefonica group. He serves as co-chair at the Open Optical Packet Transport group in the Telecom Infra Project. He has co-authored more than 200 publications, six patents and contributed to IETF and ONF. Moreover, he is the editor of the book Elastic Optical Networks: Architectures, Technologies, and Control (308 pages, Springer 2016). His research interests include the integration of Internet services over IP/MPLS and optical networks and control plane technologies (PCE, SDN, GMPLS).\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{victor.jpg}}]%
{Cristyan Manta-Caro} (M.Sc. 2007 - PhD (c)) currently serves as Solutions Manager and Managing Consultant at Wipro Technologies Ltd within the Comms EGM BU. He is responsible for structuring and leading transformation projects for Digital and Telecommunications providers. With over 15 years of experience in managing, optimizing, analyzing telecommunications and Information Technology IT infrastructures with primary vendors and CSP. He received his Master of Science and Electronics Engineering degree from the District University of Bogota Francisco Jos\'e de Caldas. His research interests include SDN architectures, Future Internet, DevNet \& NetDevOps, Cloud Technologies for IoT and the Web of Things WoT.\end{IEEEbiography}

\begin{IEEEbiography}Arturo Mayoral López de Lerma is a Technology Expert in Transport Networks at the Global Systems \& Network department of Telefónica GCTIO. He received the Ph.D. degree in telecommunications engineering from the Universitat Politècnica de Catalunya (UPC) in 2019. His  research  interests  include  optical network design and Software Defined Networking (SDN). He is author or co-author on over 50+ journals and conference papers. He graduated in Telecommunications Engineering by the Universidad Autónoma de Madrid in 2013 and he started his professional career in 2012, as undergraduate researcher in Telefonica I+D (R\&D) where developed his Final Career’s Project, awarded with the Best Final Project Prize by the Official College of Telecommunication Engineers (COIT).\end{IEEEbiography}

\begin{IEEEbiography}Oscar González de Dios received his M.S. degree in telecommunications engineering and Ph.D. degree (Hons.) from the University of Valladolid, Spain. He has 19 years of experience in Telefonica I+D, where he has been involved in a number of European research and development projects (recently, STRONGEST, ONE, IDEALIST, and Metro-Haul). He has coauthored over 100 research papers and 10 IETF RFCs. He is currently the head of SDN Deployments for Transport Networks, Telefonica Global CTIO. His main research interests include photonic networks, flexi-grid, interdomain routing, PCE, automatic network configuration, end-to-end MPLS, performance of transport protocols, and SDN. He is currently active in several IETF Working Groups and is the Co-Chair of TIP CANDI WG.\end{IEEEbiography}

\begin{IEEEbiography}Edward Echeverry is Head Of Transport (IP and Optical Network) in Telefonica Colombia. Electronic Engineer, Telecommunications Specialist with a 15+ years of experience in the field. High technical skills and advanced experience in the design, planning and implementation of 3G/4G mobile, IP/MPLS and new generation optical networks, as well as in management and deployment of projects. Lead PoC concept tests of an end-to-end SDTN system including the different layers of IP \& Optical transport network that allowed us to define the use cases of topology and services L1/L2/L3. The tests looked at the use of SBI/NBI T-API IETF-Based interfaces. His research interests include emerging network automation technologies and SDTN architectures.\end{IEEEbiography}

\begin{IEEEbiography}Juan Pedro Fernández-Palacios Giménez received the MS in Telecommunications Engineering from Polytechnic University of Valencia in 2000. In Sept. of 2000 he joined Telefonica I+D where his research activities where focused on the design of new data and control plane architectures for IP over optical networks. He is author of 6 patents filled in Europe and US and more than 70 publications in conferences and journals. He was coordinator of two European research projects on optical transport networks (MAINS and IDEALIST) between 2011 and 2014. In 2013 he joined the Telefonica Global CTO office as Head of Transport. In 2016, he also took this position in Telefonica-O2 Germany. Since June 2017 he is leading the Integrated Transport Centre, a global organization in Telefonica in charge of defining the strategic network planning and technology for IP, DWDM, MW and satellite networks.\end{IEEEbiography}

\begin{IEEEbiography}Janne Karvonen (M.Sc.(Tech.) 1993 Helsinki University of Technology) is a Senior Software Architect at Infinera Corporation. He works in the Systems Architecture Group, focusing on Software Defined Networking Technologies and IP/MPLS Network Management Systems. He has over 30 years of experience in Software Engineering and more than 20 years of experience in Telecommunications Network Management Systems, covering both optical and packet based technologies. His research interests include SDN technologies for multi-layer, multi-domain and multi-vendor networks, with special focus on SDN API technologies, Multi-Layer Path Computation Algorithms and utilization of Machine Learning in SDN networks.\end{IEEEbiography}

\begin{IEEEbiography}Jutta Kemppainen received her Master of Science (Tech.) in 1999 from Helsinki University of Technology (now part of Aalto University). She works as Senior Principal Product Manager at Infinera, managing Infinera multi-layer, multi-domain and multi-vendor transport network automation solutions. She has over 20 years of experience of telecommunications software automation products and has been concentrating on Software-Defined Networking (SDN)-based solutions in the last 7+ years. During this time Kemppainen has been co-operating with 70+ network providers, including many of the largest and technically most advanced in the industry, in designing and defining requirements for practical transport network automation solutions.\end{IEEEbiography}

\begin{IEEEbiography}Natalia Isabel Maya Perfetti is an Electronics and Telecommunications engineer graduated from Universidad del Cauca, Colombia back in 2018; thence, she has been working as a network planning engineer in Infinera Colombia where she supports different tasks related to DWDM Network Planning. For the last year she has also been responsible for the testing of the SDTN solution in the field trial environment.\end{IEEEbiography}

\begin{IEEEbiography}Ricard Vilalta (Girona, 1983) graduated in telecommunications engineering in 2007 and received a Ph.D. degree in telecommunications in 2013, both from the Universitat Politècnica de Catalunya (UPC), Spain. He joined CTTC in 2010, and he is a senior researcher in the Optical Networks and Systems Department. He is an active contributor in several standardization bodies such as ONF (OTCC), ETSI (NFV, ZSM), and IETF (CCAMP, TEAS). He is also a member of the technical steering team of Open Transport Configuration \& Control in ONF. He is leading open source contributions and features in ETSI Open Source MANO (OSM) with special focus on 5G technologies.\end{IEEEbiography}

>>>>

\begin{IEEEbiography}
[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/1010179793S.jpg}}]%
{Samier Barguil} (M.Sc. 2018). PhD Candidate from the Universidad Autonoma de Madrid. Electronic Engineer from the District University of Bogot\'a Franscisco José de Caldas and Master in Science in Industrial Automation of the Universidad Nacional de Colombia. Currently is the IP SDN Technical Leader at Wipro Technologies Ltd.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/victor.jpg}}]%
{Víctor López} (M.Sc. 2005 - Ph.D. 2009) is a Technology Expert at Systems and Network Global Direction in Telefónica gCTIO. He works on the global IP and transport processes of the Telefonica group. He serves as co-chair at the Open Optical Packet Transport group in the Telecom Infra Project. He has co-authored more than 200 publications, six patents and contributed to IETF and ONF. Moreover, he is the editor of the book Elastic Optical Networks: Architectures, Technologies, and Control (308 pages, Springer 2016). His research interests include the integration of Internet services over IP/MPLS and optical networks and control plane technologies (PCE, SDN, GMPLS).\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/cristyan_manta.jpeg}}]%
{Cristyan Manta-Caro} (M.Sc. 2007 - PhD (c)) currently serves as Solutions Manager and Managing Consultant at Wipro Technologies Ltd within the Comms EGM BU. He is responsible for structuring and leading transformation projects for Digital and Telecommunications providers. With over 15 years of experience in managing, optimizing, analyzing telecommunications and Information Technology IT infrastructures with primary vendors and CSP. He received his Master of Science and Electronics Engineering degree from the District University of Bogota Francisco Jos\'e de Caldas. His research interests include SDN architectures, Future Internet, DevNet \& NetDevOps, Cloud Technologies for IoT and the Web of Things WoT.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/arturomayoral.png}}]%
{Arturo Mayoral López de Lerma} is a Technology Expert in Transport Networks at the Global Systems \& Network department of Telefónica GCTIO. He received the Ph.D. degree in telecommunications engineering from the Universitat Politècnica de Catalunya (UPC) in 2019. His  research  interests  include  optical network design and Software Defined Networking (SDN). He is author or co-author on over 50+ journals and conference papers. He graduated in Telecommunications Engineering by the Universidad Autónoma de Madrid in 2013 and he started his professional career in 2012, as undergraduate researcher in Telefonica I+D (R\&D) where developed his Final Career’s Project, awarded with the Best Final Project Prize by the Official College of Telecommunication Engineers (COIT).\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/ogondio.png}}]%
{Oscar González de Dios} received his M.S. degree in telecommunications engineering and Ph.D. degree (Hons.) from the University of Valladolid, Spain. He has 19 years of experience in Telefonica I+D, where he has been involved in a number of European research and development projects (recently, STRONGEST, ONE, IDEALIST, and Metro-Haul). He has coauthored over 100 research papers and 10 IETF RFCs. He is currently the head of SDN Deployments for Transport Networks, Telefonica Global CTIO. His main research interests include photonic networks, flexi-grid, interdomain routing, PCE, automatic network configuration, end-to-end MPLS, performance of transport protocols, and SDN. He is currently active in several IETF Working Groups and is the Co-Chair of TIP CANDI WG.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/Edward_Echeverry.jpg}}]%
{Edward Echeverry} is Head Of Transport (IP and Optical Network) in Telefonica Colombia. Electronic Engineer, Telecommunications Specialist with a 15+ years of experience in the field. High technical skills and advanced experience in the design, planning and implementation of 3G/4G mobile, IP/MPLS and new generation optical networks, as well as in management and deployment of projects. Lead PoC concept tests of an end-to-end SDTN system including the different layers of IP \& Optical transport network that allowed us to define the use cases of topology and services L1/L2/L3. The tests looked at the use of SBI/NBI T-API IETF-Based interfaces. His research interests include emerging network automation technologies and SDTN architectures.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/juan_pedro.png}}]%
{Juan Pedro Fernández-Palacios Giménez} received the MS in Telecommunications Engineering from Polytechnic University of Valencia in 2000. In Sept. of 2000 he joined Telefonica I+D where his research activities where focused on the design of new data and control plane architectures for IP over optical networks. He is author of 6 patents filled in Europe and US and more than 70 publications in conferences and journals. He was coordinator of two European research projects on optical transport networks (MAINS and IDEALIST) between 2011 and 2014. In 2013 he joined the Telefonica Global CTO office as Head of Transport. In 2016, he also took this position in Telefonica-O2 Germany. Since June 2017 he is leading the Integrated Transport Centre, a global organization in Telefonica in charge of defining the strategic network planning and technology for IP, DWDM, MW and satellite networks.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/janne_karvonen_640x640.jpg}}]%
{Janne Karvonen} (M.Sc.(Tech.) 1993 Helsinki University of Technology) is a Senior Software Architect at Infinera Corporation. He works in the Systems Architecture Group, focusing on Software Defined Networking Technologies and IP/MPLS Network Management Systems. He has over 30 years of experience in Software Engineering and more than 20 years of experience in Telecommunications Network Management Systems, covering both optical and packet based technologies. His research interests include SDN technologies for multi-layer, multi-domain and multi-vendor networks, with special focus on SDN API technologies, Multi-Layer Path Computation Algorithms and utilization of Machine Learning in SDN networks.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/jutta_685x685.jpg}}]%
{Jutta Kemppainen} received her Master of Science (Tech.) in 1999 from Helsinki University of Technology (now part of Aalto University). She works as Senior Principal Product Manager at Infinera, managing Infinera multi-layer, multi-domain and multi-vendor transport network automation solutions. She has over 20 years of experience of telecommunications software automation products and has been concentrating on Software-Defined Networking (SDN)-based solutions in the last 7+ years. During this time Kemppainen has been co-operating with 70+ network providers, including many of the largest and technically most advanced in the industry, in designing and defining requirements for practical transport network automation solutions.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/natalia_maya.jpg}}]%
{Natalia Isabel Maya Perfetti} is an Electronics and Telecommunications engineer graduated from Universidad del Cauca, Colombia back in 2018; thence, she has been working as a network planning engineer in Infinera Colombia where she supports different tasks related to DWDM Network Planning. For the last year she has also been responsible for the testing of the SDTN solution in the field trial environment.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figs/Bio/vilalta.jpg}}]%
{Ricard Vilalta} graduated in telecommunications engineering in 2007 and received a Ph.D. degree in telecommunications in 2013, both from the Universitat Politècnica de Catalunya (UPC), Spain. He joined CTTC in 2010, and he is a senior researcher in the Optical Networks and Systems Department. He is an active contributor in several standardization bodies such as ONF (OTCC), ETSI (NFV, ZSM), and IETF (CCAMP, TEAS). He is also a member of the technical steering team of Open Transport Configuration \& Control in ONF. He is leading open source contributions and features in ETSI Open Source MANO (OSM) with special focus on 5G technologies.\end{IEEEbiography}
